---
title: "R Notebook"
output: html_notebook
---

## What are our goals?
### 1. Find who are people spending time with in HM (gender, married/single).
### 2. What are people doing when they feel happy maybe different catagories?.
### 3. Number of sentences.
### 4. Several data we could use, country, gender, age, marital, parenthood.

```{r}

library(shiny)
runExample("01_hello")
runExample("02_text")
runExample("03_reactivity")
runExample("04_mpg")
runExample("11_timer")
```

```{r}
library(tidyverse)
library(tidytext)
library(ggplot2)
library(tm)

```

## The goal is to find some interesting points based on gender difference.
```{r warning = FALSE}
hm_data <- read_csv("./output/processed_moments.csv")

urlfile <- 'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
dem_data <- read_csv(urlfile)

new_hm_data <- merge(dem_data, hm_data, by = "wid", all = FALSE)
new_hm_data <- unique(new_hm_data)
new_hm_data <- new_hm_data[c(1,7,15,2,3,4,5,6,8,9,10,11,12,13,14,16)]

table(new_hm_data$country)
table(new_hm_data$gender)
table(new_hm_data$marital)
table(new_hm_data$parenthood)
table(new_hm_data$predicted_category)
table(new_hm_data$num_sentence)

```

```{r}
f_data <- new_hm_data[new_hm_data$gender == "f",] %>% drop_na(predicted_category)
m_data <- new_hm_data[new_hm_data$gender == "m",] %>% drop_na(predicted_category)
o_data <- new_hm_data[new_hm_data$gender == "o",] %>% drop_na(predicted_category)

```

```{r female}
ggplot(f_data)+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "female") +
  xlab(label = NULL)


ggplot(filter(f_data, marital == "married"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "married female") +
  xlab(label = NULL)

ggplot(filter(f_data, marital == "single"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "single female") +
  xlab(label = NULL)

ggplot(filter(f_data, marital == "divorced"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "divorced female") +
  xlab(label = NULL)

ggplot(filter(f_data, marital == "separated"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "separated female") +
  xlab(label = NULL)

ggplot(filter(f_data, marital == "widowed"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "widowed female") +
  xlab(label = NULL)
```

```{r}
ggplot(m_data)+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "male") +
  xlab(label = NULL)

ggplot(filter(m_data, marital == "married"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "married female") +
  xlab(label = NULL)

ggplot(filter(m_data, marital == "single"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "single female") +
  xlab(label = NULL)

ggplot(filter(m_data, marital == "divorced"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "divorced female") +
  xlab(label = NULL)

ggplot(filter(m_data, marital == "separated"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "separated female") +
  xlab(label = NULL)

ggplot(filter(m_data, marital == "widowed"))+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "widowed female") +
  xlab(label = NULL)

```

```{r}
ggplot(o_data)+
  geom_bar(aes(x = predicted_category, fill = predicted_category)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "other") +
  xlab(label = NULL)  
```

### Trying to find different words used by male and female
### What's the first word that male and female prefer to use in sentences
### Who are more perferable of long sentences.

```{r}
f_corpus <- VCorpus(VectorSource(f_data$cleaned_hm))

# f_tf <- TermDocumentMatrix(f_corpus, control = list(removePunctuation = TRUE)) %>%             findMostFreqTerms(n = 2)
f_bag_of_words <- as_tibble(f_data$cleaned_hm) %>% 
  unnest_tokens(word, value)

f_word_count <- f_bag_of_words %>%
  count(word, sort = TRUE)

m_bag_of_words <- as_tibble(m_data$cleaned_hm) %>% 
  unnest_tokens(word, value)

m_word_count <- m_bag_of_words %>%
  count(word, sort = TRUE)
```

